Learning and Reputation under Monopoly and Duopoly: \\A Competing Bandits Approach

### 2018-08-23 paper/competing_bandits.tex
updates to tex file

What about for the entrant? The results are not consistent across priors and are summarized as follows:
\begin{enumerate}
\item Needle In Haystack - $TS > DG, DEG$
\item Heavy Tail - $DG > TS, DEG$
\item Uniform - $DG \sim DEG > TS$
\end{enumerate}
The raw results can be found in the GitHub appendix and though they are not consistent, it is interesting to note that on the priors where we see the relative reputation cost for $TS$ we have that $DG$ is preferred to $TS$ and for the priors where we see that exploration is not costly, we have that $TS$ is preferred to $DG$.

@@

Tables \ref{rep_erase} and \ref{info_erase} display the results of these experiments. Maintaining the data or reputation advantage alone still allows the incumbent to retain a significant portion of the market. The main interesting finding here, which is robust across priors for this parameterization, is that information serves as a larger barrier to entry than reputation. One possible intuition for this is that, for Heavy Tail, the information acquired after the $X$ rounds under $TS$ is sufficient so that it becomes relatively easier for $TS$ to recover the reputation loss compared to the information loss, but since $DEG$ and $DG$ learn slower and they've acquired less information over the $X$ rounds relative to $TS$ there is less of an informational advantage.

>>>>

What about for the entrant? The results are not the same across priors and are summarized as follows:
\begin{enumerate}
\item Needle In Haystack - $TS > DG, DEG$
\item Heavy Tail - $DG > TS, DEG$
\item Uniform - $DG \sim DEG > TS$
\end{enumerate}
The raw results can be found in the GitHub appendix and though they are not same across priors, it is interesting to note that on the priors where we see the relative reputation cost for $TS$ we have that $DG$ is preferred to $TS$ and for the priors where we see that exploration is not costly, we have that $TS$ is preferred to $DG$.

@@

Tables \ref{rep_erase} and \ref{info_erase} display the results of these experiments. Maintaining the data or reputation advantage alone still allows the incumbent to retain a significant portion of the market. The main interesting finding here, which is robust across priors for this parameterization, is that information serves as a larger barrier to entry than reputation when the incumbent plays $TS$. One possible intuition for this is that, for Heavy Tail, the information acquired after the $X$ rounds under $TS$ is sufficient so that it becomes relatively easier for $TS$ to recover the reputation loss compared to the information loss, but since $DEG$ and $DG$ learn slower and they've acquired less information over the $X$ rounds relative to $TS$ there is less of an informational advantage.
